---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# confx

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/confx)](https://CRAN.R-project.org/package=confx)
<!-- badges: end -->

Extends the scope of [{config}](https://www.github.com/rstudio/config) by offering path-like retrieval, queries for
unnamed config entities and referencing of entities. Config file content can be
cached in-memory and can then either be retrieved from cache or from file as
desired.

## Installation

Development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# GitHub dependencies
remotes::install_github("rappster/valid")

# Actual package
remotes::install_github("rappster/confx")
```

## Usage

### TL;DR

Suppose you have a config file `config.yml` in your package's root directory,
you either call

```{r, eval=FALSE}
conf_get("path/to/named/entity")
```

or 

```{r, eval=FALSE}
conf_get("path/to/unnamed/entity/with/query/<query>")
```

depending on what type of config entity you want to retrieve (named vs. unnamed
entity)

For more detailed explanation of the package continue reading

### Demo preliminaries

```{r}
library(confx)
```

The package ships with a demo YAML config file:

```{r}
(path_to_config <- fs::path_package("confx", "configs/config.yml"))
```

You can use this file by setting the following environment variable:

```{r}
Sys.setenv(R_CONFIG_DIR = fs::path_package("confx", "configs"))
```

### Get named entities

Entire config content:

```{r}
conf_get()
```

Entity `host`:

```{r}
conf_get("host")
```

Entity `host` but from different config environment:

```{r}
conf_get("host", config = "prod")
```

Entity `host/server_001`:

```{r}
conf_get("host/server_001")
```

Entity `host/server_001/url`

```{r}
conf_get("host/server_001/url")
```

### Get unnamed entities

For unnamed entities (which parse into unnamed lists), you can specify a query consisting of a standard R expression written out as a string:

```{r}
conf_get("settings_versions/id == 'v1'")
```

```{r}
conf_get("settings_versions/valid_from >= '2020-03-01'")
```

```{r}
conf_get("settings_versions/
  valid_from >= '2020-03-01' & 
  valid_until >= '2020-10-01'")
```

**DISCLAIMER**

When I said *standard R expressions*, this does not yet reflect the full picture as I started with simple expressions as defined in `valid_operators_logical()`

```{r}
confx:::valid_operators_logical()
```

In future releases, you will also (hopefully) be able to write something like
this:

```{r}
conf_get("settings_versions/
  stringr::str_detect(content, 'HELLO')")
```

### Entity references

TODO
